An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-09-23 CMPSpaper_writing/CMPSpaper_writing.Rmd
fixed an error in the plot

p.seg_252_plot <- table.252.cmps_seg.long %>%
  ggplot(aes(x = seg_length +3*as.numeric(factor(Metric))-9)) +
  geom_segment(aes(xend =  seg_length +3*as.numeric(factor(Metric))-9,
               y = value, yend = 0, colour = Metric)) + 
  geom_point(aes(y =  value, color = Metric), 
             alpha = 0.8,
             position=position_dodge(width = 0.5), size = 3.5) +
  scale_x_continuous(breaks = table.252.cmps_seg$seg_length, 
                     minor_breaks = NULL) +
  theme_bw() +
  theme(legend.position="none") +
  ggtitle("Results for Hamby 252") +
  ylab("Sum of Squares Ratio") + 
  xlab("Segment Length") +
  scale_colour_manual(values=cols_2, labels = labels) +
  scale_fill_manual(values=cols_1, labels = labels)

@@

p.seg_plot <- table.cmps_seg.long %>%
  ggplot(aes(x = seg_length+3*as.numeric(factor(Metric))-9)) +
  geom_segment(aes(xend = seg_length+3*as.numeric(factor(Metric))-9, 
                   y = value, yend= 0, color=Metric),
               position=position_dodge(width = 0.6)) +
  geom_point(aes(y =  value, color = Metric), 
             alpha = 0.8,
             position=position_dodge(width = 0.5), size = 3.5) +
  facet_grid(.~study, scales = "free_x") +
  scale_x_continuous(breaks = breaks_fun, 
                     minor_breaks = NULL) +
  theme_bw() +
  theme(legend.position = "bottom") +
  ylab("Sums of Squares Ratio") + 
  xlab("Segment length") +
  scale_colour_manual(values=cols_2, labels = labels) +
  scale_fill_manual(values=cols_1, labels = labels)

>>>>

p.seg_252_plot <- table.252.cmps_seg.long %>%
  ggplot(aes(x = seg_length +3*as.numeric(factor(Metric))-9)) +
  geom_segment(aes(xend =  seg_length +3*as.numeric(factor(Metric))-9,
               y = value, yend = 0, colour = Metric)) + 
  geom_point(aes(y =  value, color = Metric), 
             alpha = 0.8,
             position=position_dodge(width = 0.5), size = 3.5) +
  scale_x_continuous(breaks = table.252.cmps_seg$seg_length, 
                     minor_breaks = NULL) +
  theme_bw() +
  # theme(legend.position="none") +
  ggtitle("Results for Hamby 252") +
  ylab("Sum of Squares Ratio") + 
  xlab("Segment Length") +
  scale_colour_manual(values=cols_2, labels = labels) +
  scale_fill_manual(values=cols_1, labels = labels)

@@

p.seg_plot <- table.cmps_seg.long %>%
  mutate(
    Metric = factor(Metric,
                    levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar"))
  ) %>% 
  ggplot(aes(x = seg_length+3*as.numeric((Metric))-9)) +
  geom_segment(aes(xend = seg_length+3*as.numeric((Metric))-9, 
                   y = value, yend= 0, color=Metric),
               position=position_dodge(width = 0.6)) +
  geom_point(aes(y =  value, color = Metric), 
             alpha = 0.8,
             position=position_dodge(width = 0.5), size = 3.5) +
  facet_grid(.~study, scales = "free_x") +
  scale_x_continuous(breaks = breaks_fun, 
                     minor_breaks = NULL) +
  theme_bw() +
  theme(legend.position = "bottom") +
  ylab("Sums of Squares Ratio") + 
  xlab("Segment length") +
  scale_colour_manual(values=cols_2, labels = labels) +
  scale_fill_manual(values=cols_1, labels = labels)
